\documentclass{homework}

\title{CS382 Project 2}
\author{B Smith}

\begin{document}

\maketitle
\tableofcontents

\section{Division of Labor}
\subsection{Dale}
\begin{itemize}
    \item Wrote map.ts
    \item Wrote check-in document
    \item Future tasks:
    \item document map class
\end{itemize}
\subsection{Patrick}
\begin{itemize}
    \item Wrote graph.ts
    \item Future tasks:
    \item document graph class
\end{itemize}
\subsection{B}
\begin{itemize}
    \item created repository/Bun project structure
    \item code contributions/fixes
    \item parts of design document
    \item Future tasks:
    \item Breadth-first search
    \item document BFS
\end{itemize}

\section{Plan}
We plan to check in next week to make sure everything is being worked on.
We've already made good progress; we will likely finish up the design document next week.
Note that we weren't really given enough time to start on the breadth-first search section, due to the canceled classes and my own (Dale) slow progress on the map class.

\section{Technical overview}
This project is written in TypeScript, which is a typed superset of JavaScript.
We chose TypeScript because we wanted a language that's imperative, isn't Python (as all group members expressed a strong dislike for it), and is easy to pick up if you don't already know it.
We're using the Bun JavaScript runtime since it's reasonably simple and supports TypeScript out of the box.

\subsection{Installation}
To install Bun, follow the instructions on \url{https://bun.sh/docs/installation}.
Then, run \texttt{bun install} in the project root to install dependencies, and run \texttt{bun run index.ts} to run the program.

\subsection{Graph usage}
The \texttt{graph.ts} file contains our implementation of a key-value graph data structure.
It uses two hashmaps, one for vertices and another for edges - the vertices map holds keys and values, and the edges map holds a pair of two keys and the associated weight.

\end{document}
